%iffalse
\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass{article}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
\usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                             
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage{multicol}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}{Example}[section]
\newtheorem{definition}[problem]{Definition}
\newcommand{\BEQA}{\begin{eqnarray}}
\newcommand{\EEQA}{\end{eqnarray}}
\newcommand{\define}{\stackrel{\triangle}{=}}
\theoremstyle{remark}
\newtheorem{rem}{Remark}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{Software Assignment}
\author{EE224BTECH11044 - Muthyala koushik% <-this % stops a space
}
\date{}
\maketitle
\bigskip

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}

\section{Introduction}
Given a vector A, an eigenvalue $\lambda$ such that there exists an non-zero vector $x$(eigenvector),$$Ax=\lambda x$$ To find $\lambda$(eigenvalues) of matrix by solving the characteristic equation $$\det(A-\lambda I)$$

\section{Chosen Algorithm: QR Algorithm}
The QR algorithm is an iterative method for computing the eigenvalues of a matrix. A matrix $A$ is converted into a product of Orthogonal Matrix $Q$ and an upper triangular matrix $R$ and then transforming the matrix iteratively to converge into triangular matrix. And the diagonal elements are eigenvalues.\\
$$A=QR,A_1=RQ$$
$A_1=RQ,R=Q^{-1}$ gives $A_1=Q^{-1}AQ$ we say that $A$ and $A_1$ are similar matrices and have same eigenvalues
$$Ax=\lambda x$$
lets put $A_1$ insted of $A$
$$Q^{-1}AQx=\lambda x$$
$$AQx=\lambda Qx,Qx=y$$
$$Ay=\lambda y$$
so,we now know that $A$ and $A_1$ has same eigen values, repeatedly applying QR decomposition to RQ eventually leads to  an upper triangular matrix \\\\
Each transformation $A_k=R_kQ_k$ shifts the non-diagonal elements of $A_k$ closer to zero, resulting in a matrix that looks more and more like an upper triangular matrix after several iterations. \\
The diagonal elements of this upper triangular matrix are the eigenvalues of the original matrix $A$.

\subsection{Algorithm Description}
The QR algorithm follows these steps:
\begin{enumerate}
    \item Perform QR decomposition on $A$ to obtain $Q$  and $R$.
    \item Update $A$ using $A_1 = RQ$.
    \item Check for convergence by monitoring the off-diagonal elements.
    \item Repeat until the off-diagonal elements are below a specified tolerance or a maximum number of iterations is reached.
\end{enumerate}

\section{Time Complexity Analysis}
The QR algorithm for eigenvalue computation has a time complexity of $O(n^3)$ per iteration, where $n$ is the dimension of the matrix. This complexity arises to perform QR decomposition, involves matrix multiplication and Gram-Schmidt orthogonalization.


\section{Other Insights}
\subsection{Memory Usage}
The QR algorithm requires $O(n^2)$ space to store matrices $Q$, $R$, $A$, and intermediate results. This memory usage is reasonable for moderately sized matrices but may become a limitation for very large matrices.

\subsection{Convergence Rate}
The convergence rate of the QR algorithm depends on the matrix. It converges faster for symmetric matrix. For matrices with closely spaced or degenerate eigenvalues, the convergence can be slow.

\subsection{Suitability for Different Matrices}
The QR algorithm is particularly well-suited for dense, symmetric matrices. For Asymmetric  matrices the algorithm converge more slowly can improve using Hessenberg form

\section{Comparison of Algorithms}
\subsection{Power Iteration}
The Power Iteration method is a simple algorithm for finding the largest eigenvalue of a matrix. It has a time complexity of $O(n^2)$ per iteration, making it efficient for large matrices but unsuitable for computing all eigenvalues. It also converges slowly, especially when the largest eigenvalue is only slightly greater in magnitude than the others.

\subsection{Lanczos Algorithm}
The Lanczos algorithm is an efficient method for computing eigenvalues of large, sparse, symmetric matrices. It reduces the problem to a smaller tridiagonal matrix, significantly improving efficiency. The time complexity is $O(kn^2)$, where $k$ is the number of iterations. Primarily designed for symmetric matrices.

\subsection{Jacobi Method}
High accuracy for symmetric matrices. The method converges slowly for non-symmetric matrices.It has a time complexity of $O(n^3)$ per iteration. Generally slower than other methods for non-symmetric or large matrices.

\subsection{Comparison Summary}
\begin{itemize}
    \item \textbf{Time Complexity}: The QR algorithm has $O(n^3)$ complexity, while Power Iteration is $O(n^2)$, Jacobi is $O(n^3)$ and Lanczos is $O(kn^2)$.
    \item \textbf{Accuracy}: The QR algorithm is accurate for all eigenvalues but may require many iterations. Power Iteration is accurate only for the largest eigenvalue, Lanczos is efficient and accurate for sparse matrices , while Jacobi provides very accurate results for symmetric matrices.
    \item \textbf{Suitability}: The QR algorithm is best for dense, symmetric matrices. Power Iteration is suitable for finding a single dominant eigenvalue, Jacobi is preferred for symmetric matrices and Lanczos is preferred for large, sparse systems.
\end{itemize}

\section{Conclusion}
The QR algorithm is widely used method for eigenvalue computation, especially for dense matrices. However, for large and sparse matrices, more specialized algorithms like Lanczos provide better efficiency and performance. Understanding the properties of the matrix is crucial in selecting the appropriate method.

\end{document}
